---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# tripleblind

The goal of **tripleblind** is to allow for easy anonymization of the data before EDA to reduce biases.


**VERY EARLY WIP, expect mayor changes and the framework falls into place**

## Installation

You can install **tripleblind** from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("EmilHvitfeldt/tripleblind")
```

## Example

Under the hood it will label data that can be anonymized.

```{r example}
library(tripleblind)

strip(iris$Sepal.Length)

strip(iris$Species)

strip(sample(c(TRUE, FALSE), 10, replace = TRUE))
```

In the final release should be working on full datasets

```{r cars}
out <- purrr::map(iris, strip)
purrr::map_df(out, "data")

purrr::map(out, "conversion")
```
